\documentclass[14pt]{extarticle}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{relsize}%
\graphicspath{ {../chap11/} }
\usepackage[top=1in, bottom=0.75in, left=0.75in, right=0.75in]{geometry}
\newcommand*{\Scale}[2][4]{\scalebox{#1}{\ensuremath{#2}}}%
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\definecolor{bg}{RGB}{255,249,227}


\begin{document}

\section*{Math 208 Final Exam Review}


\subsection*{Final Exam on 12/21, Monday at 10:00am to Noon}
\textbf{I will post an announcement and send out emails with procedure details and links  to the exam by Friday, 12/17. Make certain to check your email and Canvas}
\\\\
PDF must be submitted via Canvas by 12:30PM.

\subsection{Final Exam Procedures}
The Final will be done virtually on Collaborate Ultra. You will be required to have video ON while taking the exam, so make certain it will work for you beforehand.
\\\\
You will receive via email a link to your final exam session between 9:00am and 9:30am. Log into the session about 10 minutes prior to the scheduled time. You will then be given instructions and informed where to download the exam.
\\\\
During the exam, you must keep your camera on. Make sure you have a quiet location with a good Internet connection from which to work. If you have a question during the exam, raise your hand and I will visit your room and talk with you. Please understand that there will be about 60 other persons taking this exam simultaneously.
\\\\
You have about two hours to complete the exam. You will then have an extra 30 minutes, until 12:30PM, to convert your exam to a PDF and submit it via Canvas. Do not delay on this and if you have any problems contact me immediately. Late work will NOT be accepted.
\\\\
The submission deadline is 12:30PM.

\subsection{Chapter 3}
\begin{itemize}
	\item Compound interest (1)
	\item APY (1)
\end{itemize}
Review exercises 
\begin{itemize}
	\item page 171: 17, 61
	\item page 145: 51, 53
\end{itemize}

\subsection{Chapter 9}
\begin{itemize}
	\item Limits (2)
	\item Marginal analysis (4)
\end{itemize}
Review exercises
\begin{itemize}
	\item page 543: 60, 61, 65*(a)(b), 66(a)(b), 67(a)(b)
	\item page 543: 87, 88(a), 90(b)
	\item page 538: 43*(a)(b), 44(a)(b)
\end{itemize}

\subsection{Chapter 10}
\begin{itemize}
	\item Differentiate and simplify (10)
	\item Equation of line (2)
	\item Find x where tangent is horizontal (1)
	\item Elasticity of demand (4)
\end{itemize}
Review exercises 
\begin{itemize}
	\item page 605: 15, 16, 18, 19, 37
	\item page 570: 9, 11 15, 29, 51, 53, 71, 73
	\item page 580: 21,27, 31, 32*, 39, 57, 63, 67
	\item page 605: 8, 9, 10*, 11, 41(b)*
	\item page 601: 51, 55
\end{itemize}

\subsection{Chapter 11}
\begin{itemize}
	\item First and second derivatives (1)
	\item Sign chart: extrema and points of inflection (3)
	\item Sketch the graph (1)
\end{itemize}
Review exercises 
\begin{itemize}
	\item page 686: 21*, 22, 23
\end{itemize}

\cleardoublepage

\end{document}
