\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\graphicspath{ {../chap09/} }
\usepackage[top=1in, bottom=0.75in, left=0.75in, right=0.75in]{geometry}
\newcommand*{\Scale}[2][4]{\scalebox{#1}{\ensuremath{#2}}}%
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\definecolor{bg}{RGB}{255,249,227}


\begin{document}
	
\begin{center} {\large How to score points in Math 208}\end{center}

There are still many ways to get points and raise your score in this course.
\begin{itemize}
	\item 200 points: The cumulative final
	\item 18 points: Six remaining homework assignments
	\item 15 points: Participation and attendance points remaining
	\item 8 points: extra credit points remaining
\end{itemize}


\subsection*{Final Exam on 1/21/2020}
You will need to know the algebra of:
\begin{itemize}
	\item exponents ($x^{-3/2}$)
	\item polynomials ($p(x) = x^3 + x^{-3/2} - 10$)
	\item rational functions ($p(x)/p(x)$)
	\item exponential and logarithm ($e^x - \ln(x)$)
\end{itemize}
Additionally, you should know the materials we have or will cover this semester.
\begin{itemize}
	\item Chapter 3: Interest and compound interest
	\item Chapter 4: Systems of linear equations, augmented matrices, Gauss-Jordan, Matrix operations, Inverse matrix, Matrix equations
	\item Chapter 5: Linear inequalities, corner points, minimize or maximize
	\item Chapter 8: Probability, Union and intersection, Conditional probability, Bayes formula
	\item Chapter 9: Limits and derivatives
	\item Chapter 10 Derivative of e and ln, product rule, quotient rule, chain rule, demand
	\item Chapter 11: Graphical meaning of derivatives, optimization
\end{itemize}

\subsection*{Participation and attendance}
\begin{itemize}
	\item For all of the virtual discussions, I expect you to attend and will make a note of attendance. So to get the points, show up.
	\item I expect you to come prepared for the discussion. That means you have watched the lecture video and my 10 minute intro video. You have thought about the question asked and are ready to contribute to group work.
	\item The group work we do in the discussion will often be homework problems.
	\item If you don't get what is going on, raise your hand and ask questions.
\end{itemize}
 
\subsection*{Extra credit}
\begin{itemize}
	\item Visit me during office hours for up to 2 points
	\item Each of the remaining 6 homeworks have an extra credit problem. These review Chapters 4, 5, and 8.
\end{itemize}



\cleardoublepage






\end{document}
