\documentclass[]{article}
\usepackage{graphicx}
%\graphicspath{ {../chap04/} }
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage[normalem]{ulem}

\begin{document}
	
\url{https://www.freefileconvert.com/tex-html}

\section*{5/17/2021}
\subsection*{202}
TEMPLATE

As requested, there is an answer template available for the finals exam. Find it under "Submit FINAL EXAM here".

I hope you are studying well and have your 2-sided note sheet with formulae and etc ready to go.

\section*{5/15/2021}
\subsection*{711}
FINAL REMINDERS

A reminder that during your studies, you should create a double-sided note sheet to use during the exam. The Final Exam is closed book and notes.

Also, due to our technical-difficulty shortened review on Thursday, I did not cover some important problems. Please review book problems page 210 numbers 31-33 and page 281 numbers 21 and 33.

For page 281 \#21, the corner points of the solution region are (0,0), (0,4), (4,3), and (5,0).

For page 281 \#33, the corner points of the solution region are (3,8), (8,10), and (12, 2). Recall, the corner points are really all that is needed to maximize or minimize an objective function.

Finally, I will have my regular office hours on Tuesday from 2-4pm.


\section*{5/11/2021}
\subsection*{202}
FINAL EXAM

Your Final Exam is on Tuesday, 5/18, from 6:30PM to 8:30PM. As previously, it will be on Collaborate Ultra and you will have an additional 30 minutes to scan and turn in your exam.
\subsection*{711}
FINAL EXAM

Your Final Exam is on Wednesday, 5/19, from 3PM to 5PM. As previously, it will be on Collaborate Ultra and you will have an additional 30 minutes to scan and turn in your exam.

\section*{5/11/2021}
\subsection*{202}
\subsection*{711}
EXAMS 1, 2, AND 3 STUDY PROBLEMS

Professor Sparks has recommended the following questions from the book to study for the Final Exam. These are the same questions as shown in the lecture section announcement.

Exam 1

p. 145 37,41,47,53 \\
p. 185  \\
p.196 15, 23, 49, 53 \\
p. 207 43 \\
p. 221 4,8 ,43,17, 19 \\
p. 234 43,61 \\
p. 241 21,45 \\

Exam 2

p.263 15, 49 \\
p. 269 33 \\
p. 281 29 \\
p. 367 15,16,29,55 \\
p. 375 14,23, 25,35 \\
p. 387 7,17,22,20, 43,39 \\
p.407 47, 58 \\

Exam 3

P 471 21, 25,27,42,62 \\
P 483 39 \\
P 510 25 \\
P 521 19, 35, 47, 59, 67, 77 \\
p 537 33



\section*{5/11/2021}
\subsection*{202}
\subsection*{711}
SI REVIEW WITH HALLE

Your Supplemental Instruction Leader, Halle B., will be holding a review for your upcoming exam (link to room below). This review is offered by the Student Success Center (SSC) at UWM. 

-----\\
Live Exam Review \\
Date: Friday, May 14th\\
Time: 2-4pm

Collaborate Ultra Room Link: Math 208 - Halle B.
\url{https://us.bbcollab.com/collab/ui/session/guest/128bcc21a3614b8cabbb575a1896555a}

\section*{4/29/2021}
\subsection*{202}
\subsection*{711}
MATH 208 DALTON EVALUATION

We will take some class time to complete evaluations, but please make certain to complete yours regardless. This instructor feed back is very helpful to me and I do appreciate your comments and critiques.

Check your email for your personalized link.

\section*{4/8/2021}
\subsection*{202}
\subsection*{711}
EXTRA CREDIT SECTION 10.4

Section 10.4 has a 5 point extra credit problem. Please see Week 14 in May for details.

\section*{4/8/2021}
\subsection*{202}
\subsection*{711}
DROP DEADLINE

The deadline to drop a course at UWM is this Sunday. For this class, the most accurate grade estimate is given by your performance on the exams.

\section*{4/8/2021}
\subsection*{202}
\subsection*{711}
EXAM REVIEW

I have posted a review sheet for Exam 3. Study this prior to Tuesday. On Tuesday, I will not do a full formal review but mostly answer your questions.

SI REVIEW

There will be a Supplemental Instruction review by Halle for the exam on Friday from 2:00 to 4:00. It will be recorded. I encourage you to attend this or view the recording. The link is https://us.bbcollab.com/collab/ui/session/guest/128bcc21a3614b8cabbb575a1896555a

\section*{4/8/2021}
\subsection*{202}
EXAM TEMPLATE AVAILABLE

A template for the next exam is available for download and printing.

\section*{4/8/2021}
\subsection*{202}
\subsection*{711}
UPDATED COURSE SCHEDULE

The course schedule has been updated to cover the remainder of the term. Also, homework through the remainder of the semester has now been posted in MyLab.

\section*{3/30/2021}
\subsection*{202}
\subsection*{711}
EXTRA CREDIT SECTION 9.4

Section 9.4 has a 5 point extra credit problem. You will need to use the four-step process and the method I talked about during the Appendix Review.

\section*{3/20/2021}
\subsection*{202}
\subsection*{711}
ENJOY SPRING BREAK

Get out and enjoy the beautiful weather we are having to start spring. See you on Tuesday, March 30.

\section*{3/17/2021}
\subsection*{202}
\subsection*{711}
COUNTING EXPLANATION

I posted a file called Counting just below the exam review. This tries to explain the 6 coats example more clearly.

\section*{3/15/2021}
\subsection*{202}
\subsection*{711}
EXAM REVIEW SHEETS AVAILABLE

I posted exam review sheets today. Review these and be prepared to ask questions during your Tuesday section.



\section*{3/13/2021}
\subsection*{202}
HOMEWORK 8.3, EXTRA CREDIT, AND EXAM QUESTIONS

Homework 8.3 is canceled! If you already submitted work, you will receive credit for that work.

\bgroup
\def\arraystretch{1.5}
\begin{tabular}{|r|r|}
	\hline
	Section & Due Date \\
	\hline
	8.1 & 3/9 \\
	\hline
	8.2 & 3/11 \\
	\hline
	\sout{8.3} & \sout{3/16} \\
	\hline
\end{tabular}
\egroup

Extra Credit of 5 points is still available but I am changing the due date to Friday, 3/19, after the exam. It is Page 455, number 44, a conditional probability problem.

Finally, there will be 15 questions on the exam, not 20. I will update the answer template to match this.



\section*{3/9/2021}
LIVE EXAM REVIEW

Your Supplemental Instruction Leader, Halle B., will be holding a review for your upcoming exam.

Live Exam Review 

Date: Monday, March 15th
Time: 3:30-5:30pm

Collaborate Ultra Room Link: Math 208 - Halle B.
\url{https://us.bbcollab.com/collab/ui/session/guest/128bcc21a3614b8cabbb575a1896555a}



\section*{3/6/2021}
EXTRA CREDIT

5 Points

This is a Conditional Probability problem

Page 455, number 44
Due 3/16/2021
	
\section*{3/04/2021}
\subsection*{711}
UPDATED HOMEWORK THROUGH BREAK

Due to pacing of lectures and the need for all exams to cover the same material, the schedule between now and break is updated. The new due dates on both Canvas and MyLab are:\\\\
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{|r|r|}
	\hline
	Section & Due Date \\
	\hline
	7.3 & 3/9 \\
	\hline
	7.4 & 3/9 \\
	\hline
	8.1 & 3/14 \\
	\hline
	8.2 & 3/16 \\
	\hline
	8.3 & 3/16??? \\
	\hline
\end{tabular}
\egroup

\subsection*{202}
UPDATED HOMEWORK THROUGH BREAK

Due to pacing of lectures and the need for all exams to cover the same material, the schedule between now and break is updated. The new due dates on both Canvas and MyLab are:\\\\
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{|r|r|}
	\hline
	Section & Due Date \\
	\hline
	8.1 & 3/9 \\
	\hline
	8.2 & 3/11 \\
	\hline
	8.3 & 3/16 \\
	\hline
\end{tabular}
\egroup

	
\section*{2/18/2021}
UPDATED COURSE SCHEDULE

The Course Schedule has been updated and may be found under Course Information. It now includes all topics up to April 15, also known as Exam 3. I have also added the matching homework into MyLab Math.

	
\section*{2/18/2021b}
ACADEMIC INTEGRITY

Hi All,

We have indications that there has been some less than 100\% honest behavior in regards to Test 1. Copying is obviously not allowed. Nor is providing answers. I believe most students do not engage in such behavior and I appreciate your integrity. I feel I should let everyone know, however, that the university takes academic dishonesty very seriously (as do I). It is important to me that every student (every instructor too) is treated fairly and equally and all have the same chances at success and excellence.

Reminder: Please be sure to show all your work on your exams in Math 208 this term.

--Professor Sparks
	
\section*{2/18/2021}
ID REMINDER

This is a reminder to have your ID ready to show me in the virtual session. I prefer your student ID but if you do not have that then another valid ID will work. You receive a link to the exam after  displaying your ID.
	
\section*{2/14/2021}
EXAM 1 REVIEW VIDEOS

I posted some problem set review videos for exam 1. These may be found under Lecture and Example Videos.
	
\section*{2/12/2021}
LIVE EXAM REVIEW

Date: Monday, February 15th \\
Time: 3:30-5:30 pm

Your Supplemental Instruction Leader, Halle Berres, will be holding a review for your upcoming exam (link to room below). This review is offered by the Student Success Center (SSC) at UWM. \url{https://us.bbcollab.com/collab/ui/session/guest/128bcc21a3614b8cabbb575a1896555a}

If you cannot attend, weekly SI sessions are available in the Ultra room indicated below, at the following times: 

Tue: 11 AM-12 PM

Wed: 10-11 AM, 4-5 PM

Thu: 12-1 PM

Fri: 2-3 PM

Room: \url{https://us.bbcollab.com/collab/ui/session/guest/128bcc21a3614b8cabbb575a1896555a}

Make an appointment:\url{https://uwm.edu/studentsuccess/make-an-appointment/}



\section*{2/5/2021}
Homework will now be due on Tuesdays and Sundays instead of the current Tuesday/Friday schedule. This means Section 4.3 is due Sunday.

This change applies to both MyLab Math and Canvas assignments.


\end{document}


