\documentclass[12pt,letterpaper]{article}
\usepackage[top=1.20cm, bottom=1.2cm]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[shortlabels]{enumitem}
\author{Gary Dalton <gdalton@uwm.edu>}

\begin{document}
\pagenumbering{gobble}
	
\begin{center} \LARGE Math 208-711 - Exam 01\end{center}%Need to change xxx to a number
\smallskip

\begin{center} \begin{tabular}{l l}
		\textbf{Date}: 2/18/2021 & \\
		\textbf{Time}: 4:45pm to 5:40pm &
		\textbf{Submission deadline}: 6:05pm\\
		\textbf{Contact}: Professor Dalton
		& \textbf{Other} Open book and notes but time limited. \\
		\textbf{Email}: gdalton@uwm.edu 
		& \qquad No Collaboration! \\
		\textbf{Tel}:(414) 810-6631
\end{tabular} \end{center}% Use your name and the current date


\section*{INSTRUCTIONS}
This exam is time-limited. That means you must submit it via Canvas by the deadline in order to receive credit. If you are having any issues submitting it on time, contact Professor Dalton immediately.
\begin{enumerate}
	\item Login and remain logged into your Collaborate Ultra virtual session. Your camera must remain on for the duration of the exam. You may be asked to show your ID and scan the room with your camera.
	\item Print the exam or use separate paper
	\begin{enumerate}[(i)]
		\item If using separate paper, layout your pages neatly and in the correct numbered order.
	\end{enumerate}
	\item Print your name at the top of the first page.
	\item Review and sign the honor pledge
	\begin{enumerate}[(i)]
		\item If using separate paper, write at the top of your exam "I understand and will abide by the honor pledge", then sign and date it.
	\end{enumerate}
	\item Complete each question on the exam
	\begin{enumerate}[(i)]
		\item Show all your work
		\item Use extra paper if needed
	\end{enumerate}
	\item Submit your exam. Make certain to allow about 20 minutes for this process.
	\begin{enumerate}[(i)]
		\item Late submissions will not be accepted.
		\item Scan or photograph your completed exam
		\item Convert your exam to a PDF file
		\item Submit the exam on Canvas.
	\end{enumerate}
\end{enumerate}

\section*{CODE OF HONOR PLEDGE}

I will not give or receive aid on this examination. I will not collaborate with others. This includes discussing the exam with students who have not yet taken it. I also understand that Professor Dalton will follow the University of Wisconsin - Milwaukee academic misconduct policies if he detects acts of academic dishonesty.
\\\\\\
Signature:\rule{8cm}{0.4pt} Date:\rule{4cm}{0.4pt}



\end{document}