\documentclass[12pt]{article}
\usepackage[top=0.75in, bottom=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\graphicspath{graphs}
\usepackage{xcolor}
\usepackage[shortlabels]{enumitem}
\usepackage{multicol}
\setlength{\columnsep}{1cm}

\title{\vspace{-10ex}Math 208 Exam 1}
\author{}
\date{\vspace{-5ex}Show ALL of your work, and clearly label each problem}

\begin{document}
\maketitle
\begin{multicols}{2}
[Some Formula]
\begin{itemize}
	\item $I=Prt$
	\item $A=P+ I$
	\item $A = P(1+ \frac{r}{m})^{mt}$
	\item $A = Pe^{rt}$
	\item $APY = (1 + \frac{r}{m})^m -1$
	\item $APY = e^r -1$
	\item $\det(M) = ad-bc$
	\item $M^{-1} = \frac{1}{\det(M)}\begin{bmatrix}
		d & -b \\
		-c & a
	\end{bmatrix}$
\end{itemize}
\end{multicols}

\begin{center}\rule{4cm}{0.4pt}\end{center}

\begin{enumerate}
\item A payday lender charges \$60 for a loan of \$500 for 15 days. Find the annual interest rate. (Use a 360-day year.)
\vspace{2.5cm}

\item Suppose \$30,000 is invested at an annual interest rate of 1.2\%.  Compute the future value after 10 years if the interest rate is compounded monthly. Round to the nearest cent.
\vspace{2.5cm}

\item Suppose an investment account has an annual interest rate of 4.3\%.  How long does it take an investment to double if interest is compounded continuously?  Round to the nearest tenth of a year.
\vspace{2.5cm}

\item If I wish to retire in 35 years with \$500,000, how much must I invest now at 2.1\% nominal interest rate compounded continuously. Round to the nearest cent.
\vspace{3.0cm}

\item How much must be invested now at UW Credit Union so that 6 years from now the
amount would be \$44,500? Assume the nominal interest rate is 3\% compounded quarterly. Round to the nearest cent.
\vspace{3.0cm}

\item Two banks have investment accounts that compound their interest differently.  Which of the two accounts has a better effective rate?
\begin{enumerate}[A)]
	\item Bank A has an interest rate of 5.3\% compounded monthly
	\item Bank B has an interest rate of 5.2\% compounded continuously
\end{enumerate}
\end{enumerate}
\vspace{3.0cm}

\begin{center}\rule{4cm}{0.4pt}\end{center}

\textbf{For all matrix operations, compute the result or if the operation is not possible, state why.}
\begin{enumerate}
\setcounter{enumi}{6}

\item Solve the following system of equations using substitution
\begin{align*}
	4x-y &= 12 \\
	-3x+4y &= 6
\end{align*}
\vspace{3.0cm}

\item  Put the following system of equations into augmented matrix form.
\begin{align*}
	\begin{array}{rrrrl}
		3x_1 &  +x_2& -x_3 & +2x_4 & =2 \\
		2x_1&  & 	+2x_3 &  & =1 \\
		-x_1&  -x_2&  &  +x_4 & = 0\\
		x_1&  +3x_2& -3x_3 & & =9
	\end{array}
\end{align*}
\vspace{2.0cm}

\item Solve the augmented matrix using Gauss-Jordan elimination
\begin{flalign*}
	\begin{bmatrix}
		3 & 1 & | & 6 \\
		2 & -2 & | & -8
	\end{bmatrix}
\end{flalign*}
\vspace{4.0cm}

\item Solve the equation $\begin{bmatrix} 1 & 2 \\ 2 & 5 \end{bmatrix} \begin{bmatrix} x_1 \\ x_2 \end{bmatrix}=\begin{bmatrix} 0 \\ 2 \end{bmatrix}$.  Using the inverse matrix method
\vspace{4.0cm}

\item Solve the following for $x$, $y$, and $z$
\[\begin{bmatrix}
3x & 2y \\ 
4z & 6
\end{bmatrix} +
\begin{bmatrix}
2 & 5 \\
z & -6
\end{bmatrix} =
\begin{bmatrix}
5 & 11 \\
25 & 0
\end{bmatrix}\]
\vspace{4.0cm}

\item Compute the resulting matrix.
\begin{align*}
\begin{bmatrix}
1 & 0 \\
-3 & -2
\end{bmatrix} -2
\begin{bmatrix}
1 & 0 \\
-3 & -2
\end{bmatrix} =
\end{align*}
\vspace{3.0cm}

\item Find $AB$, and $BA$, given that $A=\begin{bmatrix}
2 & -2 \\
0 & 1 \\
3 & 1
\end{bmatrix}$ and $B=\begin{bmatrix}
2 & 6 & 0 \\
4 & 1 & -1 \\
0 & 1 & -2
\end{bmatrix}$
\vspace{5.0cm}

\item Find
\begin{align*}
	\begin{bmatrix}
		1 & 0 & 0 \\
		0 & 1 & 0 \\
		0 & 0 & 1
	\end{bmatrix}
	\begin{bmatrix}
		0 & 5 & 4 \\
		1 & 2 & 1 \\
		0 & 3 & 5
	\end{bmatrix}
\end{align*}
\vspace{3.0cm}

\item Let $I=\begin{bmatrix} 1 & 0 \\ 0 & 1 \end{bmatrix}$, and $A=\begin{bmatrix} a & b \\ c & d \end{bmatrix}$.  Find $I^{20}AI^{3}$.
\vspace{3.5cm}

\item Use the row operations to find $A^{-1}$, or explain why it doesn't exist if \\$A= \begin{bmatrix} 4 & 8 & 1 \\ 1 & 2 & 3 \\ 5 & 10 & 1 \end{bmatrix}$
\vspace{3.5cm}

\item Solve the system of equations
\begin{align*}
    3x_1+2x_2 &= 1 \\
    -x_1-x_2 &= -1
\end{align*}
\vspace{3.0cm}

\item Find $x$, so that
\begin{align*}
	\begin{bmatrix}
		3 & 4x-1 \\
		-1 & 4x+3
	\end{bmatrix} & 
	&\text{is singular}
\end{align*}
\vspace{3.0cm}

\item Give an example of matrices $A$, and $B$ such that $AB=BA$, but $AB \neq I$
\vspace{3.0cm}

\item Give an example of matrices $A, B, C, D$ such that
\begin{enumerate}
	\item $AB$ is undefined, why is your example undefined?
	\vspace{3.0cm}
	
	\item $C+D$ is undefined, why is your example undefined?
\end{enumerate}
    
\end{enumerate}



\end{document}