\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\graphicspath{graphs}

\title{Math 208 Exam 1}
\author{Write answers NEATLY on a separate piece (or multiple pieces) of paper}
\date{Show ALL of your work, and clearly label each problem}

\begin{document}

\maketitle

\newpage
        \begin{enumerate}
        \item Suppose \$30,00 is invested at an annual interest rate of 5.2\%.  Compute the balance after 10 years if the interest rate is compounded monthly.  Round to the nearest cent if necessary.
        \item Suppose an investment account has an annual interest rate of 7.3\%.  How long does it take an investment to double if interest is compounded quarterly?  Round to the nearest tenth of a year if necessary.
        \item An investment account triples it's value after 10 years.  If the account compounds continuously, what is the interest rate?  Round to the nearest tenth of a percent if necessary.
        \item Explain (using words and symbols) the difference between simple interest, interest compounded monthly, and interest compounded continuously.  Which of the three grows the fastest?  Which grows the slowest?
        \item Three banks have investment accounts that compound their interest differently.  Which of the three accounts grows the fastest?  Which grows the slowest? \\
        A) Bank A has an interest rate of 5.6\% compounded annually \\
        B) Bank B has an interest rate of 5.3\% compounded monthly \\
        C) Bank C has an interest rate of 5.2\% compounded continuously
        \item Solve the following for $x$, $y$, and $z$
        \[\begin{bmatrix}
        3x & 2y \\ 
        4z & 6
        \end{bmatrix} +
        \begin{bmatrix}
        2 & 5 \\
        z & -6
        \end{bmatrix} =
        \begin{bmatrix}
        5 & 11 \\
        25 & 0
        \end{bmatrix}\]
        \item Compute the following matrix, or state why the operations are not possible.  $a$, $b$, $c$, and $d$ are non-zero constants \\
        \[3\begin{bmatrix}
        a & b \\
        -c & -d
        \end{bmatrix} -4
        \begin{bmatrix}
        -a & 3b \\
        4c  & d
        \end{bmatrix}\]
        \item Let $A=\begin{bmatrix}
        2 & 6 & 3 \\
        4 & 1 & -2
        \end{bmatrix}$ and $B=\begin{bmatrix}
        2 & -2 \\
        4 & 1 \\
        3 & 1
        \end{bmatrix}$
        Find $AB$, and $BA$, or state why the operation is not possible.
        \item Let $A$, $B$, and $X$ be $n \times n$ matrices, and assume $A^{-1}$, and $B^{-1}$ exist.  Solve $AXBA=BA$ for $X$.  Your answer should be in terms of $A$, $B$, $A^{-1}$ and $B^{-1}$.  State when you use the associative property and the identity matrix.
        \item Let $I=\begin{bmatrix} 1 & 0 \\ 0 & 1 \end{bmatrix}$, and $A=\begin{bmatrix} a & b \\ c & d \end{bmatrix}$.  Find $I^{20}AI^{3}$.
        \item Use the row operations to find $A^{-1}$, or explain why it doesn't exist if $A= \begin{bmatrix} 1 & 2 & 3 \\ 4 & 8 & 1 \\ 5 & 10 & 1 \end{bmatrix}$
        \item Solve the following system of equations using substitution
        \begin{align*}
        4x-y &= 12 \\
        -3x+4y &= 6
        \end{align*}
        \item  Solve the following system of equations using elimination
        \begin{align*}
            3x+2y &= 8 \\
            -6x + 4y &= 16
        \end{align*}
        \item Solve the following system of equations using Gauss-Jordan elimination
        \begin{align*}
            3x_1+x_2-x_3 &= 1 \\
            2x_1-x_2+x_3 &= 0 \\
            x_1-x_2+5x_3 &= 2
        \end{align*}
        \item Solve the equation $\begin{bmatrix} 1 & 2 \\ 2 & 5 \end{bmatrix} \begin{bmatrix} x_1 \\ x_2 \end{bmatrix}=\begin{bmatrix} 0 \\ 2 \end{bmatrix}$  Using the inverse matrix method
        \item Solve the equation 
        \begin{align}
            3x_1+2x_2-x_3 &= 1 \\
            -x_1-x_2-x_3 &= -1 \\
            6x_1+4x_2-2x_3 &=3
        \end{align}
        \item Explain (using words/graphs/symbols) what it means for a system of 2 linear equations with 2 variables to have no solution, one solution, and infinitely many solutions.
        \item Give an example of matrices $A$, and $B$ such that $AB=BA$, but $AB \neq I$
        \item Give an example of Matrices $A$, $B$ such that \\
            a) $AB$ is undefined, why is your example undefined? \\
            b) $A+B$ is undefined, why is your example undefined?
        \item Explain (using words/symbols) the relationship between a matrix equation $AX=Y$, where $A$ is an $3 \times 3$ matrix, and $X$, and $Y$ are both $3 \times 1$ matrices, and a system of three linear equations with three variables.
        \item Write your name on the upper right corner of each page, take a picture and submit your exam as a pdf on canvas.

            
        \end{enumerate}



\end{document}